---
title: "<span style='font-size: 30px;'> Box Plot Chart Analysis </span> <span style='font-size: 20px; color:gray;'>[Psychological Traits] </span>"
---
[How does personality affect the drug consumption patterns?]{style="background-color:#fdfd96;"}

[This page will present a box plot analysis examining the influence of scores obtained in five personality factors from the NEO-FFI-R questionnaire on patterns of drug consumption. The analyzed factors include **Neuroticism (N Score), Extraversion (E Score), Openness to Experience (O Score), Agreeableness (A Score), and Conscientiousness (C Score)**. A higher score indicates a greater likelihood of experiencing specific feelings within each respective category.]{style="font-size: 12pt; color: gray;"}

```{r, eval=TRUE, echo=FALSE}
drug <- read.csv("Drug_Consumption_Quantified.csv")
drug <- subset(drug, Country != "-0.28519")
drug_or <- read.csv("Drug_Consumption.csv")
drug_or <- subset(drug_or, Country != "Other")
```

## **Legal** Drugs

These three drugs (alcohol, cafeeine and nocotine) are legal in all 6 analyzed countries.

### Alcohol

#### AScore

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(AScore ~ Alcohol, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Alcohol), y = AScore)) +
  geom_boxplot() +
  labs(x = "Alcohol", y = "AScore") +
  ggtitle("Box Plot of AScore by Alcohol Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$AScore, 0.5), yend = quantile(drug_or$AScore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$AScore) - 1, label = paste("μ =", round(mean_values$AScore, 2)), vjust = 0, hjust = 0.5)
```

#### CScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Cscore ~ Alcohol, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Alcohol), y = Cscore)) +
  geom_boxplot() +
  labs(x = "Alcohol", y = "CScore") +
  ggtitle("Box Plot of CScore by Alcohol Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Cscore, 0.5), yend = quantile(drug_or$Cscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Cscore) - 1, label = paste("μ =", round(mean_values$Cscore, 2)), vjust = 0, hjust = 0.5)
```

#### EScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Escore ~ Alcohol, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Alcohol), y = Escore)) +
  geom_boxplot() +
  labs(x = "Alcohol", y = "EScore") +
  ggtitle("Box Plot of EScore by Alcohol Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Escore, 0.5), yend = quantile(drug_or$Escore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Escore) - 1, label = paste("μ =", round(mean_values$Escore, 2)), vjust = 0, hjust = 0.5)
```

#### NScore

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Nscore ~ Alcohol, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Alcohol), y = Nscore)) +
  geom_boxplot() +
  labs(x = "Alcohol", y = "NScore") +
  ggtitle("Box Plot of NScore by Alcohol Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Nscore, 0.5), yend = quantile(drug_or$Nscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Nscore) - 1, label = paste("μ =", round(mean_values$Nscore, 2)), vjust = 0, hjust = 0.5)
```

#### OScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Oscore ~ Alcohol, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Alcohol), y = Oscore)) +
  geom_boxplot() +
  labs(x = "Alcohol", y = "OScore") +
  ggtitle("Box Plot of OScore by Alcohol Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Oscore, 0.5), yend = quantile(drug_or$Oscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Oscore) - 1, label = paste("μ =", round(mean_values$Oscore, 2)), vjust = 0, hjust = 0.5)
```

### Caffeine

#### AScore

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(AScore ~ Caff, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Caff), y = AScore)) +
  geom_boxplot() +
  labs(x = "Caffeine", y = "AScore") +
  ggtitle("Box Plot of AScore by Caffeine Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$AScore, 0.5), yend = quantile(drug_or$AScore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$AScore) - 1, label = paste("μ =", round(mean_values$AScore, 2)), vjust = 0, hjust = 0.5)
```

#### CScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Cscore ~ Caff, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Caff), y = Cscore)) +
  geom_boxplot() +
  labs(x = "Caffeine", y = "CScore") +
  ggtitle("Box Plot of CScore by Caffeine Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Cscore, 0.5), yend = quantile(drug_or$Cscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Cscore) - 1, label = paste("μ =", round(mean_values$Cscore, 2)), vjust = 0, hjust = 0.5)
```

#### EScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Escore ~ Caff, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Caff), y = Escore)) +
  geom_boxplot() +
  labs(x = "Caffeine", y = "EScore") +
  ggtitle("Box Plot of EScore by Caffeine Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Escore, 0.5), yend = quantile(drug_or$Escore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Escore) - 1, label = paste("μ =", round(mean_values$Escore, 2)), vjust = 0, hjust = 0.5)
```

#### NScore

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Nscore ~ Caff, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Caff), y = Nscore)) +
  geom_boxplot() +
  labs(x = "Caffeine", y = "NScore") +
  ggtitle("Box Plot of NScore by Caffeine Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Nscore, 0.5), yend = quantile(drug_or$Nscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Nscore) - 1, label = paste("μ =", round(mean_values$Nscore, 2)), vjust = 0, hjust = 0.5)
```

#### OScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Oscore ~ Caff, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Caff), y = Oscore)) +
  geom_boxplot() +
  labs(x = "Caffeine", y = "OScore") +
  ggtitle("Box Plot of OScore by Caffeine Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Oscore, 0.5), yend = quantile(drug_or$Oscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Oscore) - 1, label = paste("μ =", round(mean_values$Oscore, 2)), vjust = 0, hjust = 0.5)
```

### Nicotine
#### AScore

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(AScore ~ Nicotine, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Nicotine), y = AScore)) +
  geom_boxplot() +
  labs(x = "Nicotine", y = "AScore") +
  ggtitle("Box Plot of AScore by Nicotine Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$AScore, 0.5), yend = quantile(drug_or$AScore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$AScore) - 1, label = paste("μ =", round(mean_values$AScore, 2)), vjust = 0, hjust = 0.5)
```

#### CScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Cscore ~ Nicotine, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Nicotine), y = Cscore)) +
  geom_boxplot() +
  labs(x = "Nicotine", y = "CScore") +
  ggtitle("Box Plot of CScore by Nicotine Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Cscore, 0.5), yend = quantile(drug_or$Cscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Cscore) - 1, label = paste("μ =", round(mean_values$Cscore, 2)), vjust = 0, hjust = 0.5)
```

#### EScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Escore ~ Nicotine, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Nicotine), y = Escore)) +
  geom_boxplot() +
  labs(x = "Nicotine", y = "EScore") +
  ggtitle("Box Plot of EScore by Nicotine Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Escore, 0.5), yend = quantile(drug_or$Escore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Escore) - 1, label = paste("μ =", round(mean_values$Escore, 2)), vjust = 0, hjust = 0.5)
```

#### NScore

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Nscore ~ Nicotine, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Nicotine), y = Nscore)) +
  geom_boxplot() +
  labs(x = "Nicotine", y = "NScore") +
  ggtitle("Box Plot of NScore by Nicotine Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Nscore, 0.5), yend = quantile(drug_or$Nscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Nscore) - 1, label = paste("μ =", round(mean_values$Nscore, 2)), vjust = 0, hjust = 0.5)
```

#### OScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Oscore ~ Nicotine, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Nicotine), y = Oscore)) +
  geom_boxplot() +
  labs(x = "Nicotine", y = "OScore") +
  ggtitle("Box Plot of OScore by Nicotine Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Oscore, 0.5), yend = quantile(drug_or$Oscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Oscore) - 1, label = paste("μ =", round(mean_values$Oscore, 2)), vjust = 0, hjust = 0.5)
```
## **Controversial** Drugs

This drug (cannabis) is legal in two analyzed countries (the United States and Canada) but illegal in four others.

### Cannabis
#### CScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Cscore ~ Cannabis, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Cannabis), y = Cscore)) +
  geom_boxplot() +
  labs(x = "Cannabis", y = "CScore") +
  ggtitle("Box Plot of CScore by Cannabis Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Cscore, 0.5), yend = quantile(drug_or$Cscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Cscore) - 1, label = paste("μ =", round(mean_values$Cscore, 2)), vjust = 0, hjust = 0.5)
```

#### EScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Escore ~ Cannabis, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Cannabis), y = Escore)) +
  geom_boxplot() +
  labs(x = "Cannabis", y = "EScore") +
  ggtitle("Box Plot of EScore by Cannabis Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Escore, 0.5), yend = quantile(drug_or$Escore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Escore) - 1, label = paste("μ =", round(mean_values$Escore, 2)), vjust = 0, hjust = 0.5)
```

#### NScore

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Nscore ~ Cannabis, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Cannabis), y = Nscore)) +
  geom_boxplot() +
  labs(x = "Cannabis", y = "NScore") +
  ggtitle("Box Plot of NScore by Cannabis Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Nscore, 0.5), yend = quantile(drug_or$Nscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Nscore) - 1, label = paste("μ =", round(mean_values$Nscore, 2)), vjust = 0, hjust = 0.5)
```

#### OScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Oscore ~ Cannabis, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Cannabis), y = Oscore)) +
  geom_boxplot() +
  labs(x = "Cannabis", y = "OScore") +
  ggtitle("Box Plot of OScore by Cannabis Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Oscore, 0.5), yend = quantile(drug_or$Oscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Oscore) - 1, label = paste("μ =", round(mean_values$Oscore, 2)), vjust = 0, hjust = 0.5)
```

## **Illegal** Drugs

These two drugs (Cocaine, Heroin) are illegal across all six analyzed countries.

### Cocaine
#### CScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Cscore ~ Coke, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Coke), y = Cscore)) +
  geom_boxplot() +
  labs(x = "Cocaine", y = "CScore") +
  ggtitle("Box Plot of CScore by Cocaine Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Cscore, 0.5), yend = quantile(drug_or$Cscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Cscore) - 1, label = paste("μ =", round(mean_values$Cscore, 2)), vjust = 0, hjust = 0.5)
```

#### EScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Escore ~ Coke, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Coke), y = Escore)) +
  geom_boxplot() +
  labs(x = "Cocaine", y = "EScore") +
  ggtitle("Box Plot of EScore by Cocaine Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Escore, 0.5), yend = quantile(drug_or$Escore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Escore) - 1, label = paste("μ =", round(mean_values$Escore, 2)), vjust = 0, hjust = 0.5)
```

#### NScore

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Nscore ~ Coke, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Coke), y = Nscore)) +
  geom_boxplot() +
  labs(x = "Cocaine", y = "NScore") +
  ggtitle("Box Plot of NScore by Cocaine Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Nscore, 0.5), yend = quantile(drug_or$Nscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Nscore) - 1, label = paste("μ =", round(mean_values$Nscore, 2)), vjust = 0, hjust = 0.5)
```

#### OScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Oscore ~ Coke, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Coke), y = Oscore)) +
  geom_boxplot() +
  labs(x = "Cocaine", y = "OScore") +
  ggtitle("Box Plot of OScore by Cocaine Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Oscore, 0.5), yend = quantile(drug_or$Oscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Oscore) - 1, label = paste("μ =", round(mean_values$Oscore, 2)), vjust = 0, hjust = 0.5)
```

### Heroin
#### CScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Cscore ~ Heroin, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Heroin), y = Cscore)) +
  geom_boxplot() +
  labs(x = "Heroin", y = "CScore") +
  ggtitle("Box Plot of CScore by Heroin Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Cscore, 0.5), yend = quantile(drug_or$Cscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Cscore) - 1, label = paste("μ =", round(mean_values$Cscore, 2)), vjust = 0, hjust = 0.5)
```

#### EScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Escore ~ Heroin, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Heroin), y = Escore)) +
  geom_boxplot() +
  labs(x = "Heroin", y = "EScore") +
  ggtitle("Box Plot of EScore by Heroin Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Escore, 0.5), yend = quantile(drug_or$Escore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Escore) - 1, label = paste("μ =", round(mean_values$Escore, 2)), vjust = 0, hjust = 0.5)
```

#### NScore

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Nscore ~ Heroin, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Heroin), y = Nscore)) +
  geom_boxplot() +
  labs(x = "Heroin", y = "NScore") +
  ggtitle("Box Plot of NScore by Heroin Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Nscore, 0.5), yend = quantile(drug_or$Nscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Nscore) - 1, label = paste("μ =", round(mean_values$Nscore, 2)), vjust = 0, hjust = 0.5)
```

#### OScore
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

mean_values <- aggregate(Oscore ~ Heroin, data = drug_or, FUN = mean)

ggplot(drug_or, aes(x = factor(Heroin), y = Oscore)) +
  geom_boxplot() +
  labs(x = "Heroin", y = "OScore") +
  ggtitle("Box Plot of OScore by Heroin Consumption Level") +
  theme(panel.border = element_rect(color = "black", fill = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  annotate("segment", x = 1:7, xend = 1:7, y = quantile(drug_or$Oscore, 0.5), yend = quantile(drug_or$Oscore, 0.5), color = "black", size = 1.2) +
  annotate("text", x = 1:7, y = min(drug_or$Oscore) - 1, label = paste("μ =", round(mean_values$Oscore, 2)), vjust = 0, hjust = 0.5)
```
